Vagueness, Noise, and Signaling

### 2015-04-16 paper/version_03/paper.tex
Added placeholder figure for example of Voronoi language. Added footnote to alert user that "imprecision" and "impairment" are the same thing and the terms are used interchangeably.

\citet{JagerMetzger2011:Voronoi-Languag} showed that the
evolutionarily stable states of sim-max games are remarkably
systematic. Their results were obtained for games with infinitely many
states in $n$-dimensional Euclidean space $\States \subseteq
\mathds{R}^n$ and a quadratic loss function for utilities
$\Utils(\mystate{1}, \mystate{2}) = - (\mystate{1} -
\mystate{2})^2$. For these games, the evolutionarily stable states are
demonstrably so-called Voronoi languages. Roughly put, a Voronoi
language is a pair of sender and receiver strategies, such that the
sender strategy partitions the state space into convex categories,
while the receiver's interpretations are the central spots in each
category. A subset $X$ of $\mathds{R}^n$ is convex if, informally put,
all points in $X$ are connected via a straight line that lies entirely
in $X$; $X$ has no gaps or dents. For example, if \States is the unit
interval and all states are equiprobable, a Voronoi language with two
messages would have the sender use one message exclusively for all
points in the lower half of the unit interval and another for all
points in the upper half; the receiver's interpretations of messages
are the central points, .25 and .75, in the respective intervals.

@@

Confusion of states should intuitively be a function of their
perceptual similarity. To make this concrete, let us assume that the
state space of the sim-max game consists of $n \ge 2$ states that are
equally spaced across the unit interval, including $0$ and $1$. The
distance $\card{\mystate{i} - \mystate{j}}$ is the objective, physical
similarity between two states $\mystate{i}$ and
$\mystate{j}$. Distance in physical space feeds into a perceptual
similarity function, as described by
\citet{Nosofsky1986:Attention-Simil}:
\begin{align*}
  \similarity(\mystate{i}, \mystate{j} \myts ; \myts \impairment) =
      \begin{cases}
    1 & \textrm{if } \impairment = 0 \textrm{ and } \mystate{i} = \mystate{j} \\
    0 & \textrm{if } \impairment = 0 \textrm{ and } \mystate{i} \neq \mystate{j} \\
 \expo \left ( -  \frac{\card{\mystate{i} - \mystate{j}}^s}{ \impairment^2} \right ) & \textrm{otherwise,} \\
    \end{cases}
\end{align*}
where $\impairment \ge 0$ is an imprecision or indiscriminability
parameter. When $\impairment=0$ agents perfectly discriminate between
states; when $\impairment \rightarrow \infty$ agents cannot
discriminate states at all. Figure~\ref{fig:NosofskySim} gives an
impression of Nosofsky-similarity for different parameter
values. Other formalizations of perceptual similarity are possible,
including ones that allow for different discriminability in different
areas of the state space, but we stick with Nosofsky's similarity
function for the time being, because it is mathematically simple, yet
an established notion in mathematical psychology.

>>>>

\citet{JagerMetzger2011:Voronoi-Languag} showed that the
evolutionarily stable states of sim-max games are remarkably
systematic. Their results were obtained for games with infinitely many
states in $n$-dimensional Euclidean space $\States \subseteq
\mathds{R}^n$ and a quadratic loss function for utilities
$\Utils(\mystate{1}, \mystate{2}) = - (\mystate{1} -
\mystate{2})^2$. For these games, the evolutionarily stable states are
demonstrably so-called Voronoi languages. Roughly put, a Voronoi
language is a pair of sender and receiver strategies, such that the
sender strategy partitions the state space into convex categories,
while the receiver's interpretations are the central spots in each
category. A subset $X$ of $\mathds{R}^n$ is convex if, informally put,
all points in $X$ are connected via a straight line that lies entirely
in $X$; $X$ has no gaps or dents. For example, if \States is the unit
interval and all states are equiprobable, a Voronoi language with two
messages would have the sender use one message exclusively for all
points in the lower half of the unit interval and another for all
points in the upper half; the receiver's interpretations of messages
are the central points, .25 and .75, in the respective intervals
(see Figure~\ref{fig:Voronoi-language-example} for an illustration).

\begin{figure}
  \centering
  \missingfigure{Example of Voronoi language for unit interval}
  \caption{}
  \label{fig:Voronoi-language-example}
\end{figure}

@@

Confusion of states should intuitively be a function of their
perceptual similarity. To make this concrete, let us assume that the
state space of the sim-max game consists of $n \ge 2$ states that are
equally spaced across the unit interval, including $0$ and $1$. The
distance $\card{\mystate{i} - \mystate{j}}$ is the objective, physical
similarity between two states $\mystate{i}$ and
$\mystate{j}$. Distance in physical space feeds into a perceptual
similarity function, as described by
\citet{Nosofsky1986:Attention-Simil}:
\begin{align*}
  \similarity(\mystate{i}, \mystate{j} \myts ; \myts \impairment) =
      \begin{cases}
    1 & \textrm{if } \impairment = 0 \textrm{ and } \mystate{i} = \mystate{j} \\
    0 & \textrm{if } \impairment = 0 \textrm{ and } \mystate{i} \neq \mystate{j} \\
 \expo \left ( -  \frac{\card{\mystate{i} - \mystate{j}}^s}{ \impairment^2} \right ) & \textrm{otherwise,} \\
    \end{cases}
\end{align*}
where $\impairment \ge 0$ is an impairment, imprecision or indiscriminability
parameter\footnote{We use these terms interchangeably throughout the paper.}.
When $\impairment=0$ agents perfectly discriminate between
states; when $\impairment \rightarrow \infty$ agents cannot
discriminate states at all. Figure~\ref{fig:NosofskySim} gives an
impression of Nosofsky-similarity for different parameter
values. Other formalizations of perceptual similarity are possible,
including ones that allow for different discriminability in different
areas of the state space, but we stick with Nosofsky's similarity
function for the time being, because it is mathematically simple, yet
an established notion in mathematical psychology.
